---
title: "FinalProjectAnalysisScript"
author: "Dun Fletcher Lin"
date: "2025-02-22"
output: html_document
---

### Import libraries

```{r}
library(printr) # Package used for printing out the documentation of function in the output

library(grDevices) # Package used for plotting out time series

library(tseries) # Package for Time series analysis and computational finance

library(graphics)

library(utils)

library(stats) # Package used for statistical calculations and random number generations

library(forecast) # Package used for functions that could be used for creating forecast including seasonality plot

library(ggplot2) # Package used for plotting out the the dataset
```

-----

### 1. Introduction: Includes problem statement and objective of your project.

-----

### 2. Data: Elaborate on the data used in this project with detailed description of all attributes, source of data, missing observations, etc. Describe any steps you followed to prepare the data.

#### Data Description

#### Data Source

#### Load in data

Read in file from .csv
```{r}
cyber_data <- read.csv(file = "./information-2897447-supplementary/cyber_data.csv")
```

#### Examine attributes of the data

Examine attributes of data
```{r}
numberOfColumns <- ncol(cyber_data)
cat(c('There are ', numberOfColumns, 'columns in the dataset'))
numberOfObservations <- nrow(cyber_data)
cat(c('There are', numberOfObservations, 'observations in the dataset'))
```

#### Missing observations

Generate a table which print out the following structure
columnName, hasNA, numberOfNA
```{r}
maximumLengthOfColumnName <- max(nchar(names(cyber_data)))

cat("******************\n")
cat("Summary table for missing observations: \n")
cat(c("columnName", strrep(' ', maximumLengthOfColumnName - 10), '| hasNA', ' | numberOfNA\n'))
for (column in colnames(cyber_data)) {
  hasNA <- sum(is.na(cyber_data[column])) > 0
  numberOfNA <- sum(is.na(cyber_data[column]))
  if (hasNA) {
    cat(c(column, 
          strrep(' ', maximumLengthOfColumnName - nchar(column) + 2), 
          paste('|', hasNA), 
          '   | ', 
          numberOfNA, 
          '\n'), 
        sep = '')
  }
  else {
    cat(c(column, 
          strrep(' ', maximumLengthOfColumnName - nchar(column) + 2), 
          paste('|', hasNA), 
          '  | ', 
          numberOfNA, 
          '\n'), 
        sep = '')
  }
}
cat("******************")
```

#### Data Preparation

#### Data Exploration

-----

### 3. Experimental results and Analysis: Execute algorithm (plots, ACF, PACF, Spectral Analysis, hypothesis testing, etc.), discuss results with appropriate details.

#### Initial Plot

#### ACF

#### PACF

-----

### 4. Model Selection: Select final model based on selection criteria and evaluate forecasting metrics and accuracy.


#### Final Model

#### Forecasting Metrics

#### Accuracy

-----

### 5. Conclusion and Future work: Summarize your work and draw specific conclusions from the overall final project. Describe next steps to continue working on this project. (i.e., how the model forecasting can be improved)

-----

### Cleanup task

Cleanup the variables that are defined in the environment
```{r}
rm(list = ls())
```