---
title: "FinalProjectAnalysisScript"
author: "Dun Fletcher Lin"
date: "2025-02-22"
output: html_document
---

### Import libraries

```{r}
library(printr) # Package used for printing out the documentation of function in the output

library(grDevices) # Package used for plotting out time series

library(tseries) # Package for Time series analysis and computational finance

library(graphics)

library(utils)

library(stats) # Package used for statistical calculations and random number generations

library(forecast) # Package used for functions that could be used for creating forecast including seasonality plot

library(ggplot2) # Package used for plotting out the the dataset
```

-----

### 1. Introduction: Includes problem statement and objective of your project.

-----

### 2. Data: Elaborate on the data used in this project with detailed description of all attributes, source of data, missing observations, etc. Describe any steps you followed to prepare the data.

-----

### 3. Experimental results and Analysis: Execute algorithm (plots, ACF, PACF, Spectral Analysis, hypothesis testing, etc.), discuss results with appropriate details.

-----

### 4. Model Selection: Select final model based on selection criteria and evaluate forecasting metrics and accuracy.

-----

### 5. Conclusion and Future work: Summarize your work and draw specific conclusions from the overall final project. Describe next steps to continue working on this project. (i.e., how the model forecasting can be improved)

-----

### Cleanup task

Cleanup the variables that are defined in the environment
```{r}
rm(list = ls())
```